First, I would like to thank the support of my family: my mother, for the unconditional love and for the most beautiful heart I have ever seen; my father, for the discipline and perfectionism taught to me, essential for a work like this; my brother, companion at all hours, always listening to my animated monologues about this work and many others; my girlfriend, Jade, for the patience and support during this one-year journey, in which I often had to sacrifice our moments.

Secondly, I thank my teachers during this long walk, at school and at college. Many of you motivated me and made me believe that this would be possible. Many of you have done so much more than the role of teaching, and on account of that I have created an immense respect for the profession. You are the foundation of society.

Thirdly, I would like to thank all my friends who have made this journey ever more fun. There were countless moments in which you rejoiced in my journey. In particular, my roommates, for the coexistence over the last few years. Many of the happiest memories of this time are due to you and our friendship will continue for the rest of our lives, regardless of any distance.

Fourthly, I thank the ITAndroids team for all the technical teachings and friendships I have formed. In fact, I assign to this team a large part of my training as an engineer and motivation to face complex problems. Our competitions, evenings and weekends of working are worth it and I will miss all of it.

Finally, I thank those who gave support for this work to happen: ITAndroids, for access to the code and proposition of the problem; Professor Marcos Máximo and Professor Adilson Marques da Cunha, for guidance; Intel, for providing the computational support to all the experiments and to make feasible the execution of this project.